Towards the Analysis of the Queuing System Operating in~the~Random Environment with Resource Allocation

### 2024-07-21 template/preamble/font/fontspec/cm-unicode.tex

\newfontfamily\cyrillicfont[Script=Cyrillic,Ligatures=TeX]{CMU Concrete}
\newfontfamily\cyrillicfontsf[Script=Cyrillic,Ligatures=TeX,Scale=MatchLowercase]{CMU Sans Serif}
\newfontfamily\cyrillicfonttt[Script=Cyrillic,Scale=MatchLowercase]{CMU Typewriter Text}

\setmainfont[Ligatures=TeX]{CMU Concrete}
\setsansfont[Ligatures=TeX,Scale=MatchLowercase]{CMU Sans Serif}
\setmonofont[Scale=MatchLowercase]{CMU Typewriter Text}

>>>>

\setmainfont[Ligatures=TeX,Scale=MatchLowercase]{CMU Serif}
\setsansfont[Ligatures=TeX,Scale=MatchLowercase]{CMU Sans Serif}
\setmonofont[Scale=MatchLowercase]{CMU Typewriter Text}

% CMU Serif
\newfontfamily\cyrillicfont%
[Script=Cyrillic,Ligatures=TeX,Scale=MatchLowercase]%
{CMU Serif}

% CMU Sans Serif
\newfontfamily\cyrillicfontsf%
[Script=Cyrillic,Ligatures=TeX,Scale=MatchLowercase]%
{CMU Sans Serif}

% CMU Typewriter Text
\newfontfamily\cyrillicfonttt%
[Script=Cyrillic,Scale=MatchLowercase]%
{CMU Typewriter Text}
